Spin canonical divisors of log stacky curves

### 2015-06-28 stacky_write_up/spin_cring.tex
fix g0 example with a_1, b_1 nonzero

Let $I$ be the ideal generated by these relations in
$k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}]$. Under grlex with
$x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$, the initial ideal of $I$ is \todo{This will only be the case if $a_1,b_1 \neq 0$. We can definitely make this hold if we set up the variables in the right way, but I'm not sure if it's always true.}
\[
	in_\prec(I) = \langle x_{5, 1}^2, x_{7, 1}^2 \rangle
\]

>>>>

\noindent
and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
have that
\[
	a_2 x_{3, 1} x_{7, 1} = a_3 x_{3, 1} x_{7, 2}
\]

\noindent
However, $x_{3, 1} x_{7, 1}$ has pole orders $(3, 4, 3)$ and
$x_{3, 1} x_{7, 2}$ has pole orders $(3, 3, 4)$ so their
coefficients must be zero for this equality to hold. We have a
similar pole-order consideration in forcing $b_1$ to be nonzero.

Let $I$ be the ideal generated by these relations in
$k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}]$. Under grlex with
$x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$, the initial
ideal of $I$ is
\[
	in_\prec(I) = \langle x_{5, 1}^2, x_{7, 1}^2 \rangle
\]

\noindent
since $a_1$ and $b_1$ are nonzero.
